\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \vspace{2pt}\item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNormal}[1]{
  \vspace{2pt}\item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/crickash/}{\Large Akash Dubey}} & Email : \href{mailto:akashrdubey19@gmail.com}{akashrdubey19@gmail.com}\\
  \href{https://www.linkedin.com/in/crickash/}{LinkedIn, }\href{https://github.com/codec-akash}{Github, }\href{https://stackoverflow.com/users/15859365/akash-dubey}{Stack Overflow} & Mobile : 8422022076 \\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Twid - Pay with rewards}{Bangalore, IN}
      {Software Engineer - Flutter}{Aug 2023 - Present}
      \resumeItemListStart
        \resumeItemNormal
          {Architect the front-end of the complete UPI module SDK using \textbf{Clean Architecture}.}
        \resumeItemNormal
          {Added \textbf{UPI processes} with UI implementation for Pay with UPI id, phone number, Account transfer, self transfer, mandate and UDIR dispute with Juspay SDk.}
        \resumeItemNormal
          {\textbf{Custom Paint animations} for Transaction status screen after a payment for seamless user experience.}
        \resumeItemNormal
          {Handled \textbf{Root Check} and fixed memory leak from the app which resulted in the seamless process of Audit approval for \textbf{stability and security }of the app}
        \resumeItemNormal
          {Implemented \textbf{App Integrity Check} to disable side-load of app through apk improving the security of the app.}
        \resumeItemNormal
          {Added \textbf{BBPS} integration with Pay with rewards with Twid UPI with server-side UI Architecture.}
      \resumeItemListEnd

    \resumeSubheading
      {Akudo}{Bangalor, IN}
      {Software Developer - Flutter}{Jan 2022 - July 2023}
      \resumeItemListStart
        \resumeItemNormal
          {Implemented \textbf{UPI integration from NPCI} on PPI, enabling users to seamlessly conduct UPI transactions, track transaction status, and access transaction history.}
        \resumeItemNormal
          {Boosted app \textbf{loading speed by 65\%} through parallel BLoC calls and data holders, enabling faster home screen refresh and enhancing user experience.}
        \resumeItemNormal
          {Integrated \textbf{mobile recharge} with automated plan expiration reminders and \textbf{real-time recharge order status using sockets}. Implemented comprehensive \textbf{search functionality across all JSON keys} for efficient recharge plan searching}
        \resumeItemNormal
          {Implemented \textbf{video KYC} with a non-linear flow and 
          \textbf{document blur detection using TensorFlow ML Kit}. Added a paywall feature with direct debit functionality through wallet.}
        \resumeItemNormal
          {Added \textbf{Referral Program} in which user can send a \textbf{Dynamic Link} to help onboard another user and earn rewards. Implemented user tracking for the app journey for milestone rewards}
      \resumeItemListEnd

    \resumeSubheading
      {Akudo - Intern}{Bangalore, IN}
      {Flutter Developer Intern}{July 2021 - Jan 2022}
      \resumeItemListStart
        \resumeItem{User Retention/Acquisition}
          {Integrated SDKs such as Mixpanel, MoEngage, and AppsFlyer to enhance user analytics, engagement, and tracking, providing valuable insights for business growth and user retention.}
        \resumeItem{Log Collection}
          {Implemented Sentry for log collection , enabling efficient monitoring and issue resolution, ensuring stable and reliable app performance.}
        \resumeItem{Design Revamp}
          {Performed a comprehensive UI/UX redesign of the entire app, resulting in a substantial improvement in user experience.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Tricket App}
      {A Cricket score guess app with P2P support for leaderboard and winnings. The score was guessed in the spell of 4-5 overs}{\href{https://apps.apple.com/in/app/tricket-analyse-win/id1667156965}{App Store, } {\href{https://play.google.com/store/apps/details?id=in.tricket.tricketApp&hl=en_IN}{Play Store}}}
    \resumeSubItem{Basket Ball Counter}
      {Designed a basketball net which is able to count the number of successful baskets done using arduino and the score was shown in app and basket}{\href{https://www.hackster.io/171442/basketball-counting-machine-7a9907}{Article}}
    \resumeSubItem{Universal Clipboard}
      {Created a Clipboard management dashboard which syncs the device clipboard over other platform to give a apple ecosystem usage for android. tech - Flutter, Firebase}{\href{https://github.com/codec-akash/clipy}{Clipy}}
      \resumeSubItem{Verify Extension}
      {{\href{https://verifyextensions.com}{ verify extensions}} is a chrome extension to manage and verify, what all permission other extensions are using.  tech - HTML, JS, Node}{\href{https://github.com/codec-akash/verify-extension}{github},{\href{https://chromewebstore.google.com/detail/extension-verifier/majhflhllmkmghpoiidahbgklieikjnc}{ extension}}
      \resumeSubItem{Resume}
      {have build this resume using LaTeX}{\href{https://github.com/codec-akash/LaTeX-Resume}{Akash Resume}}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Dart, Java, Python, JS, SQL, Rust}
     \hfill
     \textbf{Technologies}{: Flutter, Android Studio, Firebase, GraphQl}
   }
 \resumeSubHeadingListEnd

 %-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Manav Rachna University}{Delhi NCR}
      {BTech CSE}{2018 -- 2022}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
